Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-08-17 article/draft.tex
add the Shayan part

%\subsection{Data related recommendations}

@@

>>>>

@@

Although it is currently impossible to verify permanent deletions using social media data, their effects can be observed using an adapted methodology.
Following the Capitol riots in January 2021, Twitter has announced the suspension of more than 70,000 accounts related to QAnon.
\footnote{\url{https://blog.twitter.com/en_us/topics/company/2021/protecting--the-conversation-following-the-riots-in-washington--}} 
A journalist has recently investigated the effects of this measure by counting the number of times some hashtags specific to the QAnon movement have been used over time, such as \#QAnon or \#WWG1WGA.
A drastic reduction in hashtag use was found when comparing the first quarter of 2021 with the first quarter of 2021.
\footnote{\url{https://twitter.com/Shayan86/status/1394742784683298818}}
Thus, counting specific hashtag use over time allows to indirectly observe permanent suspensions on Twitter, and other similar methodologies can be found for the other platforms.
